---
title: "TokenLink"
output: github_document
date: '2022-05-05'
editor_options: 
  chunk_output_type: console
---



Link two data sets using tokens or words in common between them.


```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

```


# Install Libraries
```{r read_souces, echo = FALSE, warning = FALSE, message = FALSE}
source('R/tokenify.R')
```


```{r Install, eval = FALSE, warning = FALSE}
source('R/tokenify.R')
devtools::install_github("csps-efpc/TokenLink")
```
## Load Libraries

```{r libraries_load, message = FALSE,  warning = FALSE, results=FALSE}
library(reclin)
library(tidyverse)
library(purrr)

data_dir <- 'data'
```



## Load in two datasets

```{r load_data}

orig_dat <- 
  data_dir |> 
  file.path('generated_dataset.csv') |>
  read_csv() |>
  replace_na(list(company_name = '', 
                  address = '', 
                  first_name = '', 
                  last_name = '', 
                  age = 0 
                  ))|>
  mutate_all(as.character)

edited_dat <- 
  data_dir |> 
  file.path('generated_dataset_random_edits.csv') |>
  read_csv() |>
  replace_na(list(company_name = '', 
                  address = '', 
                  first_name = '', 
                  last_name = '', 
                  age = 0 
                  )) |>
  mutate_all(as.character)




bind_cols(orig_dat, edited_dat |> rename_all(\(x){paste0(x,"_edited")})) |> 
  {\(.)select(., order(colnames(.)))}() |>
  sample_n(5) |> 
  knitr::kable(caption = 'original and edited data')

```

## Block Pairs by First Name or Last Name is the same, as well any company_name or address fields that have a word in common that is not to common.

```{r block_pairs}
blocked_pairs <- reclin_pair_blocking(x = orig_dat,
                                      y = edited_dat, 
                                      blocking_var = c('first_name', 'last_name'), #Block on Any of these Columns
                                      token_types =  c('company_name', 'address'), #Block on Any of these tokens
                                      col_nms_x = c('company_name', 'address'),    # Column Names
                                      col_nms_y =  c('company_name', 'address'),   # Column Names
                                      min_token_u_prob = 0.0000784)               # min u_prob to consider blocking on

blocked_pairs |>
  as_tibble() 

```


## Generate Reclin EM Scores


```{r reclin_scores}

# Compare pairs in Reclin using First and last name
p <- reclin::compare_pairs(blocked_pairs, 
                   by = c('first_name', 'last_name'),
                    default_comparator = jaro_winkler(0.9))

m <- problink_em(p)
p <- score_simsum(p, var = "sim_sum")
p <- score_problink(p, model = m, var = "scores", type  = 'all')

p |>
  sample_n(5) |>
  knitr::kable(caption = 'Show scores cenerated from Reclin')
```

## Refine the priori from reclin as a posterior taking into acount aditional information

```{r refine}

refined_p <- 
  refine_posterior(p = p, 
                   x_dat = orig_dat, 
                   y_dat = edited_dat, 
                   weights_nm = 'scores_weight',
                   args_x = list(col_nms = c('company_name', 'address')),
                   args_y = list(col_nms = c('company_name', 'address')),
                   token_types = c('company_name', 'address')
                   )

refined_p |> 
  mutate(is_same = (x == y)) |>
  mutate(delta_belief = posterior - priori) |> 
  ggplot(aes(y = delta_belief, x = priori,  color = is_same )) + 
  geom_jitter(alpha = 0.05, width = 0.05, height = 0.05) +
  geom_hline(yintercept=0, linetype="dashed", color = "black", size = 1.25) +
  scale_x_continuous(labels = scales::percent) +
  scale_y_continuous(labels = scales::percent) +
  labs(title = 'How much do the token columns change our belief in the Match?',
       y = 'Change in Belief', 
       color = 'Actually the same')

```


